Selective electroporation of the viral envelope

### 2021-05-19 documents/pure_electroporation.tex
An obvious discrepancy

\footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels. In both cases, destructive process involve differential charging of the external shell (the spacecraft itself) against an internal shell (the reaction wheels), producing a potential difference across a highly resistive layer (a layer of grease on the ball bearings)}

@@

>>>>

%\footnote{It is amusing to draw parallels between electroporation and Bialke et al's reports on spacecraft reaction wheels. In both cases, destructive process involve differential charging of the external shell (the spacecraft itself) against an internal shell (the reaction wheels), producing a potential difference across a highly resistive layer (a layer of grease on the ball bearings)}

@@

software used

Written in texst
